decompr: GVC decomposition in R

### 2015-01-29 draft.Rnw
add refs, line breaks, recompile after merge

The data is set up in order to illustrate the benefits of the decompositions.
That is, we follow the flows of intermediate goods through a fictional GVC and show how the readily available gross trade flows differ from the decomposed value added flows.
To this end, we construct the elements of the input-output tables such that we have two countries and two industries that focus on upstream tasks, which means they focus on supplying other industries, and one industry and one country that is specialized in downstream tasks, that is it serves mainly final demand.
In our example the upstream industries are Agriculture and Textiles while the downstream industry in Transport Equipment.
Similarly, Argentina and Turkey represent upstream countries with Germany being located downstream within this specific value chain.

@@

The derivation of the Wang-Wei-Zhu decomposition is significantly more technical than the source decomposition since it splits gross exports up more finely. This is why we present here only the final equation for a two country one industry model (equation 22 in WWZ) and refer the interested reader to the original paper by Wang, Wei, and Zhu (2014). The key idea is to use the Leontief insight and extend it using additional information from ICIOs on the final usage and destination of the exports (e.g. re-imported vs. absorbed abroad).

@@

%    \begin{adjustwidth}{-1.15in}{-1.15in}

@@

%  \end{adjustwidth}

>>>>

The data is set up in order to illustrate the benefits of the decompositions.
We do this by following the flows of intermediate goods through a fictional GVC and showing how the readily available gross trade flows differ from the decomposed value added flows.
To this end, we construct the elements of the input-output tables such that we have two countries and two industries that focus on upstream tasks, which means they focus on supplying other industries, and one industry and one country that is specialized in downstream tasks,i.e.~it serves mainly final demand.
In our example the upstream industries are Agriculture and Textiles while the downstream industry in Transport Equipment.
Similarly, Argentina and Turkey represent upstream countries with Germany being located downstream within this specific value chain (see \cref{tab:leather}.

@@

The derivation of the Wang-Wei-Zhu decomposition is significantly more technical than the source decomposition since it splits gross exports up more finely.
This is why we present here only the final equation for a two country one industry model (equation 22 in WWZ) and refer the interested reader to the original paper by Wang, Wei, and Zhu (2014).
The key idea is to use the Leontief insight and extend it using additional information from ICIOs on the final usage and destination of the exports (e.g. re-imported vs. absorbed abroad).

@@

@@
